### 2025-01-31 products/manuscript/Manuscript.qmd
commit

---
title: "Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)"
author: "Yufei Wu"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

The structure below is one possible setup for a manuscript, or a general data analysis project (including the course project). Adjust as needed. 
You don't need to have exactly these sections, but the content covering those sections should be addressed.

This uses MS Word as output format. [See here](https://quarto.org/docs/output-formats/ms-word.html) for more information. You can switch to other formats, like html or pdf. See [the Quarto documentation](https://quarto.org/) for other formats.

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

**Authors**

* Yufei Wu$^{1}$ (ORCID: 0009-0003-5051-0623)

**Author affiliations**

1. Department of Chemistry, University of Georgia, Athens, GA, USA.

$\land$ Corresponding author: yufeiwu@uga.edu

$\dagger$ Disclaimer: The opinions expressed in this article are the
author's own and don't reflect their employer.

{{< pagebreak >}}

# Summary/Abstract
_Write a summary of your project._

{{< pagebreak >}}

# Introduction

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_
H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [H1BVisaProgram2016]. It requires the employee to have a bachelor's degree or equivalent in the specific specialty. Typically, the maximun duration of an H-1B visa is six years.It is the most common work visa in the US. There are 65,000 available H-1B visas each year, with 20,000 additional visas for candidates with a master's or doctorate degree from a U.S. institution. If there are more than 65,000 applications, USCIS will run a lottery to decide who can file an H-1B petition. As USCIS is receiving more and more H-1B registration these years, it's harder for a foreign worker to get an H-1B visa. The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [LaborConditionApplication2025]. The LCA contains essential details such as job title, wage, and location about the proposed H-1B employment. Therefore, analyzing the LCA data can provide some ideas on the H-1B application status.

## Description of data and data source
_Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section._
The data is H1B LCA Disclosure Data (2020-2024) from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data). It contains LCA disclosure datasets from U.S. Department of Labor, covering the period from 2020 to 2024. It includes information such as case status, job title, Standard Occupational
Classification (SOC) title, location, and wages.

## Questions/Hypotheses to be addressed
_State the research questions you plan to answer with this analysis._
This analysis will primarily focus on certified cases. The key research questions to be examined include:
Distribution Analysis:
What is the distribution of certified cases across various features such as SOC titles, locations, wages, and employer names?
Which SOC titles, states, and employers have the highest and lowest number of certified cases?
Variable Relationships:
How do wages vary across different states, SOC titles, and employers?
Employment Trends and Remote Work Patterns:
How have employment patterns evolved over time?
What trends can be observed in remote work prevalence before and after the pandemic?
Predictive Modeling:
Can a predictive model be developed to estimate wages based on job-related and employer-specific features?
Which factors contribute most significantly to wage determination in certified cases?

To cite other work (important everywhere, but likely happens first in introduction), make sure your references are in the bibtex file specified in the YAML header above and have the right bibtex key. Then you can include like this:

Examples of reproducible research projects can for instance be found in [@mckay2020; @mckay2020a].

{{< pagebreak >}}

# Methods

_Describe your methods. That should describe the data, the cleaning processes, and the analysis approaches. You might want to provide a shorter description here and all the details in the supplement._
The data will be reduced to include obeservations with certified case status and visa class of H-1B. Variable will only include RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE.

## Schematic of workflow

Sometimes you might want to show a schematic diagram/figure that was not created with code (if you can do it with code, do it). @fig-schematic is an example of some - completely random/unrelated - schematic that was generated with Biorender.
We store those figures in the `assets` folder.

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
#| echo: FALSE
knitr::include_graphics(here("assets","antigen-recognition.png"))
```

## Data aquisition
_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._
The dataset used in this analysis was obtained from Kaggle. The data was downloaded in CSV format.

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

The raw data import and cleaning will be conducted seprately since the dataset is large.

## Statistical analysis
_Explain anything related to your statistical analyses._
Various plots will be made to visualize the data. Linear regression will be used to analyze the relationship between variables. Machine learning methods will be used as modeling technique.

{{< pagebreak >}}

# Results

## Exploratory/Descriptive analysis

_Use a combination of text/tables/figures to explore and describe your data. Show the most important descriptive results here. Additional ones should go in the supplement. Even more can be in the R and Quarto files that are part of your project._

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below. I generally recommend the `here` package.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

## Basic statistical analysis

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

## Full analysis

_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here._

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

{{< pagebreak >}}

# Discussion

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

## Strengths and Limitations
_Discuss what you perceive as strengths and limitations of your analysis._

## Conclusions
_What are the main take-home messages?_

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like.

{{< pagebreak >}}

# References

### 2025-01-31 products/manuscript/Manuscript.qmd
commit

@@
 _Provide enough background on your topic that others can understand the why and how of your analysis_
-H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [H1BVisaProgram2016].
+H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [@H1BVisaProgram2016].
 It requires the employee to have a bachelor's degree or equivalent in the specific specialty.
@@
 As USCIS is receiving more and more H-1B registration these years, it's harder for a foreign worker to get an H-1B visa.
-The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [LaborConditionApplication2025].
+The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [@LaborConditionApplication2025].
 The LCA contains essential details such as job title, wage, and location about the proposed H-1B employment.

### 2025-01-31 products/manuscript/Manuscript.qmd
revise

@@
 ## General Background Information
-_Provide enough background on your topic that others can understand the why and how of your analysis_
+
 H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [@H1BVisaProgram2016].
@@
 ## Description of data and data source
-_Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section._
+
 The data is H1B LCA Disclosure Data (2020-2024) from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data).
@@
 ## Questions/Hypotheses to be addressed
-_State the research questions you plan to answer with this analysis._
+
 This analysis will primarily focus on certified cases. The key research questions to be examined include:
@@
 
-_Describe your methods. That should describe the data, the cleaning processes, and the analysis approaches. You might want to provide a shorter description here and all the details in the supplement._
 The data will be reduced to include obeservations with certified case status and visa class of H-1B.
@@
 ## Data aquisition
-_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._
+
 The dataset used in this analysis was obtained from Kaggle. The data was downloaded in CSV format.

### 2025-01-31 products/manuscript/Manuscript.qmd
data clean

@@
 
-The raw data import and cleaning will be conducted seprately since the dataset is large.
+```{r}
+# load packages
+library(here)
+library(dplyr)
+
+# load raw data
+LCAraw <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))
+
+# get the overview of the data
+dim(LCAraw)
+head(LCAraw)
+
+# clean the data
+LCAdata <- LCAraw %>%
+  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B") %>%
+  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)
+
+# take a look at the processed data
+head(LCAdata)
+
+# save as rds
+save_data_location <- here::here("data","processed-data","LCAdata.rds")
+saveRDS(LCAdata, file = save_data_location)
+
+```
 

### 2025-02-07 products/manuscript/Manuscript.qmd
fix errors when rendering the word file

--- 2025-01-31 products/manuscript/Manuscript.qmd
@@
 ## Data import and cleaning
-_Write code that reads in the file and cleans it so it's ready for analysis.
-Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts.
-If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g.
-as supplement in a paper).
-All materials, including files that contain code, should be commented well so everyone can follow along._
+Since the dataset for this project is too large to upload to GitHub, I reduced its size and saved the smaller version as an RDS file, treating it as the raw data.
+Here's the code I used to reduce size:
 
-The raw data import and cleaning will be conducted seprately since the dataset is large.
+ # load packages
+ library(here)
+ library(dplyr)
+ # load raw data
+ LCAraw1 <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))
+ # Shrink the data
+ colnames(LCAraw1)
+ LCAraw <- LCAraw1 %>%
+   select(CASE_STATUS, VISA_CLASS, RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE,   WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)
+ # Save as rds
+ save_data_location <- here::here("data","raw-data","LCAraw.rds")
+ saveRDS(LCAraw, file = save_data_location)
+
+```{r}
+# load packages
+library(here)
+library(dplyr)
+
+# load raw data
+LCAraw <- readRDS(here("data", "raw-data", "LCAraw.rds"))
+
+# get the overview of the data
+dim(LCAraw)
+head(LCAraw)
+
+# Keep only the certified case and H-1B visa, and remove these two column
+LCAdata <- LCAraw %>%
+  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B")%>%
+  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)
+
+# take a look at the processed data
+dim(LCAdata)
+head(LCAdata)
+
+```
 

### 2025-02-21 code/processing-code/processingfile.qmd
part 2 commit 1

---
title: "Data cleaning"
author: "Yufei Wu"
output: html_document
---

## Remark
Since the dataset for this project is too large to upload to GitHub, I reduced its size and saved the smaller version as an RDS file, treating it as the raw data. Here's the code I used to reduce size:

 # load packages
 library(here)
 library(dplyr)
 # load raw data
 LCAraw1 <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))
 # Shrink the data
 colnames(LCAraw1)
 LCAraw <- LCAraw1 %>%
   select(CASE_STATUS, VISA_CLASS, RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, WAGE_UNIT_OF_PAY, PREVAILING_WAGE, PW_UNIT_OF_PAY)
 # Save as rds
 save_data_location <- here::here("data","raw-data","LCAraw.rds")
 saveRDS(LCAraw, file = save_data_location)

# Setup

```{r}
# Load packages
library(here)
library(dplyr)
library(tidyverse)
```

# Data loading

```{r}
# load raw data
LCAraw <- readRDS(here("data", "raw-data", "LCAraw.rds"))
```

# Check data

```{r}
# Get the overview of the data
dim(LCAraw)
colnames(LCAraw)
str(LCAraw)
head(LCAraw)
```

# Cleaning

```{r}
# Keep only the certified case and H-1B visa, and remove these two column
LCAdata <- LCAraw %>%
  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B")%>%
  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, WAGE_UNIT_OF_PAY, PREVAILING_WAGE, PW_UNIT_OF_PAY)

# Check missing values per column
colSums(is.na(LCAdata))

# Remove missing values
LCAdata <- LCAdata %>% drop_na()

# Check again
colSums(is.na(LCAdata)) # now it is good

# Standardize all character columns to a consistent case (except state name)
LCAdata <- LCAdata %>%
  mutate(
    SOC_TITLE = tolower(SOC_TITLE),
    EMPLOYER_NAME = tolower(EMPLOYER_NAME)
  )

# take a look at the processed data
dim(LCAdata)
head(LCAdata)
```

# Save data

```{r}
save_data_location <- here::here("data","processed-data","LCAdata.rds")
saveRDS(LCAdata, file = save_data_location)
```

### 2025-02-21 products/manuscript/Manuscript.qmd
part 2 commit 1

--- 2025-01-31 products/manuscript/Manuscript.qmd
@@
 
-The structure below is one possible setup for a manuscript, or a general data analysis project (including the course project). Adjust as needed. 
-You don't need to have exactly these sections, but the content covering those sections should be addressed.
-
-This uses MS Word as output format.
-[See here](https://quarto.org/docs/output-formats/ms-word.html) for more information.
-You can switch to other formats, like html or pdf.
-See [the Quarto documentation](https://quarto.org/) for other formats.
-
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 # load a few R packages
@@
 
-$\dagger$ Disclaimer: The opinions expressed in this article are the
-author's own and don't reflect their employer.
-
 {{< pagebreak >}}
@@
 # Summary/Abstract
-_Write a summary of your project._
 
@@
 It contains LCA disclosure datasets from U.S.
-Department of Labor, covering the period from 2020 to 2024.
-It includes information such as case status, job title, Standard Occupational
-Classification (SOC) title, location, and wages.
+Department of Labor, covering the period from 2020 to 2024, and includes information such as case status, job title, Standard Occupational Classification (SOC) title, location, and wages.
 
@@
 This analysis will primarily focus on certified cases. The key research questions to be examined include:
-Distribution Analysis:
+
+(1)Distribution Analysis:
+
 What is the distribution of certified cases across various features such as SOC titles, locations, wages, and employer names?
-Which SOC titles, states, and employers have the highest and lowest number of certified cases?
-Variable Relationships:
+
+(2)Variable Relationships:
+
 How do wages vary across different states, SOC titles, and employers?
-Employment Trends and Remote Work Patterns:
+
+(3)Employment Trends and Remote Work Patterns:
+
 How have employment patterns evolved over time?
+
 What trends can be observed in remote work prevalence before and after the pandemic?
-Predictive Modeling:
+
+(4)Predictive Modeling:
+
 Can a predictive model be developed to estimate wages based on job-related and employer-specific features?
+
 Which factors contribute most significantly to wage determination in certified cases?
-
-To cite other work (important everywhere, but likely happens first in introduction), make sure your references are in the bibtex file specified in the YAML header above and have the right bibtex key.
-Then you can include like this:
-
-Examples of reproducible research projects can for instance be found in [@mckay2020; @mckay2020a].
 
@@
 
-The data will be reduced to include obeservations with certified case status and visa class of H-1B.
-Variable will only include RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE.
+## Data aquisition and cleaning
 
-## Schematic of workflow
+The dataset used in this analysis is the H1B LCA Disclosure Data (2020-2024) from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data).
+It comprises labor condition application (LCA) disclosure records from the U.S.
+Department of Labor, covering the period from 2020 to 2024.
+The dataset includes key information such as case status, job title, Standard Occupational Classification (SOC) title, employer details, location, and wages.
 
-Sometimes you might want to show a schematic diagram/figure that was not created with code (if you can do it with code, do it).
-@fig-schematic is an example of some - completely random/unrelated - schematic that was generated with Biorender.
-We store those figures in the `assets` folder.
+To ensure data quality, the dataset was filtered to include only certified cases and those specifically related to H-1B visa applications.
 
-```{r}
-#| label: fig-schematic
-#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
-#| echo: FALSE
-knitr::include_graphics(here("assets","antigen-recognition.png"))
-```
+Additionally, the dataset was refined to include only the following essential variables:
 
-## Data aquisition
+RECEIVED_DATE (date the application was received); SOC_TITLE (occupational title classified under the SOC system); EMPLOYER_NAME (name of the employer); EMPLOYER_STATE (employer’s location); WORKSITE_STATE (location of the worksite); WAGE_RATE_OF_PAY_FROM (wage offered to the worker); WAGE_UNIT_OF_PAY (unit of pay values); PREVAILING_WAGE (prevailing wage for the job); PW_UNIT_OF_PAY (unit of pay values)
 
-The dataset used in this analysis was obtained from Kaggle. The data was downloaded in CSV format.
-
-## Data import and cleaning
-_Write code that reads in the file and cleans it so it's ready for analysis.
-Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts.
-If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g.
-as supplement in a paper).
-All materials, including files that contain code, should be commented well so everyone can follow along._
-
-The raw data import and cleaning will be conducted seprately since the dataset is large.
+Observations with missing values in the selected variables were removed. All character columns except state names were standardized to lowercase.
 
 ## Statistical analysis
-_Explain anything related to your statistical analyses._
 Various plots will be made to visualize the data. Linear regression will be used to analyze the relationship between variables. Machine learning methods will be used as modeling technique.
@@
 
-_Use a combination of text/tables/figures to explore and describe your data.
-Show the most important descriptive results here.
-Additional ones should go in the supplement.
-Even more can be in the R and Quarto files that are part of your project._
+### Univariate Analysis: Distribution Analysis
 
-@tbl-summarytable shows a summary of the data.
-
-Note the loading of the data providing a **relative** path using the `../../` notation.
-(Two dots means a folder up).
-You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path.
-You can also use the `here` R package to create paths.
-See examples of that below.
-I generally recommend the `here` package.
+The @fig-top10_soc_title displays the 10 job titles with the highest number of applications filed between 2020 and 2024, with "Software Developers, Applications" leading at over 500,000 cases.
+The @fig-top10_emp_name highlights the top 10 employers by application count, with "COGNIZANT TECHNOLOGY SOLUTIONS US CORP" topping the list at approximately 93,000 cases.
+The @fig-top10_emp_state presents the 10 states with the most applications, with California recording over 600,000 cases.
+Meanwhile, the @fig-distribution_PREV_WAGE plot illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
+```{r}
+#| label: fig-top10_soc_title
+#| fig-cap: "Top 10 Job Titles."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","top10_soc_title.png"))
+```
 
 ```{r}
-#| label: tbl-summarytable
-#| tbl-cap: "Data summary table."
+#| label: fig-top10_emp_name
+#| fig-cap: "Top 10 Employers."
 #| echo: FALSE
-resulttable=readRDS("../../results/tables/summarytable.rds")
-knitr::kable(resulttable)
+knitr::include_graphics(here("results","figures","top10_emp_name.png"))
+```
+
+```{r}
+#| label: fig-top10_emp_state
+#| fig-cap: "Top 10 Employer Locations."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","top10_emp_state.png"))
+```
+
+```{r}
+#| label: fig-distribution_PREV_WAGE
+#| fig-cap: "Distribution of Prevailing Wage."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","distribution_PREV_WAGE.png"))
+```
+
+### Bivariate Analysis
+
+The @fig-wage_by_soc_title plot shows the 10 job titles with the highest median wage, and they are all medical practitioners.
+The @fig-wage_by_employer plot highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing.
+The @fig-wage_by_state plot indicates that Washington has the highest median wage by state.
+Plots for the 10 lowest median wages are provided in Supplement Figures 1–3.
+The @fig-remote_trend_absolute plot illustrates the trend of remote work over the years.
+The number of remote work cases surged from 2019 to 2020 due to the pandemic and remained relatively stable from 2020 to 2023.
+Post-pandemic, there was a slight decline from 2023 to 2024.
+However, as remote work patterns became more established, the decrease was not significant.
+This analysis uses absolute values instead of proportions because remote work is identified based on discrepancies between employer and worksite states.
+Some remote work cases may not be captured under this definition, potentially underestimating the actual proportion.
+Therefore, absolute values provide a more accurate reflection of the remote work trend.
+
+```{r}
+#| label: fig-wage_by_soc_title
+#| fig-cap: "Top 10 Job Titles by Highest Median Wage."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","wage_by_soc_title.png"))
+```
+
+```{r}
+#| label: fig-wage_by_employer
+#| fig-cap: "Top 10 Employers by Highest Median Wage."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","wage_by_employer.png"))
+```
+
+```{r}
+#| label: fig-wage_by_state
+#| fig-cap: "Top 10 States by Highest Median Wage."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","wage_by_state.png"))
+```
+
+```{r}
+#| label: fig-remote_trend_absolute
+#| fig-cap: "Remote Work Trends Over Years."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","remote_trend_absolute.png"))
 ```
@@
 
-_To get some further insight into your data, if reasonable you could compute simple statistics (e.g.
-simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable.
-Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._
-
-@fig-result shows a scatterplot figure produced by one of the R scripts.
-
-```{r}
-#| label: fig-result
-#| fig-cap: "Height and weight stratified by gender."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
-```
-
 ## Full analysis
-
-_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc.
-This might again be code that is best placed in one or several separate R scripts that need to be well documented.
-You want the code to produce figures and data ready for display as tables, and save those.
-Then you load them here._
-
-Example @tbl-resulttable2 shows a summary of a linear model fit.
-
-```{r}
-#| label: tbl-resulttable2
-#| tbl-cap: "Linear model fit table."
-#| echo: FALSE
-resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
-knitr::kable(resulttable2)
-```
 
@@
 ## Summary and Interpretation
-_Summarize what you did, what you found and what it means._
 
 ## Strengths and Limitations
-_Discuss what you perceive as strengths and limitations of your analysis._
 
 ## Conclusions
-_What are the main take-home messages?_
-
-_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_
-
-This paper [@leek2015] discusses types of analyses.
-
-These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.
-
-Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header.
-Many more style files for almost any journal [are available](https://www.zotero.org/styles).
-You also specify the location of your bibtex reference file in the YAML.
-You can call your reference file anything you like.
 

### 2025-02-21 products/manuscript/supplement/Supplementary-Material.qmd
part 2 commit 1

---
title: "Supplement to Yufei Wu's MADA Project"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

# Overview

You can find all the supplemetary materials (figures and tables) in the supplement.

# Additional results

@tbl-sum_prev_wage shows a summary table for prevailing wage.

```{r}
#| label: tbl-sum_prev_wage
#| tbl-cap: "Summary Table for Prevailing Wage."
#| echo: FALSE
table1 = readRDS(here("results","tables","sum_prev_wage.rds"))
knitr::kable(table1)
```

@fig-bottom_wage_by_soc_title shows a bar plot of bottom 10 job titles by lowest median wage. @fig-bottom_wage_by_employer shows a bar plot of bottom 10 employers by lowest median wage. @fig-bottom_wage_by_state shows a bar plot of bottom 10 states by lowest median wage.

```{r}
#| label: fig-bottom_wage_by_soc_title
#| fig-cap: "Bottom 10 Job Titles by Lowest Median Wage."
#| echo: FALSE
knitr::include_graphics(here("results","figures","bottom_wage_by_soc_title.png"))
```

```{r}
#| label: fig-bottom_wage_by_employer
#| fig-cap: "Bottom 10 Employers by Lowest Median Wage."
#| echo: FALSE
knitr::include_graphics(here("results","figures","bottom_wage_by_employer.png"))
```

```{r}
#| label: fig-bottom_wage_by_state
#| fig-cap: "Bottom 10 States by Lowest Median Wage."
#| echo: FALSE
knitr::include_graphics(here("results","figures","bottom_wage_by_state.png"))
```

{{< pagebreak >}}

# Discussion

{{< pagebreak >}}

### 2025-02-21 code/eda-code/edacode.R

@@ -1,44 +1,257 @@
-## ---- packages --------
-#load needed packages. make sure they are installed.
-library(here) #for data loading/saving
-library(dplyr)
-library(skimr)
+# Load packages
 library(ggplot2)
+library(here)
+library(dplyr)
+library(scales)
+library(lubridate)
 
-## ---- loaddata --------
-#Path to data. Note the use of the here() package and not absolute paths
-data_location <- here::here("data","processed-data","processeddata.rds")
-#load data
-mydata <- readRDS(data_location)
 
-## ---- table1 --------
-summary_df = skimr::skim(mydata)
-print(summary_df)
-# save to file
-summarytable_file = here("results","tables", "summarytable.rds")
-saveRDS(summary_df, file = summarytable_file)
+# load data
+LCAdata <- readRDS(here("data", "processed-data", "LCAdata.rds"))
 
-## ---- height --------
-p1 <- mydata %>% ggplot(aes(x=Height)) + geom_histogram() 
-plot(p1)
-figure_file = here("results", "figures", "height-distribution.png")
-ggsave(filename = figure_file, plot=p1) 
+# Univariate Analysis: Distribution Analysis
 
-## ---- weight --------
-p2 <- mydata %>% ggplot(aes(x=Weight)) + geom_histogram() 
-plot(p2)
-figure_file = here("results", "figures", "weight-distribution.png")
-ggsave(filename = figure_file, plot=p2) 
+# Distribution of top 10 SOC_TITLE
+# Calculate counts and filter top 10 SOC_TITLE
+top10_soc <- LCAdata %>%
+  count(SOC_TITLE, sort = TRUE) %>%
+  top_n(10, n)
+# Plot the top 10 SOC_TITLE
+p1 <- ggplot(top10_soc, aes(x = reorder(SOC_TITLE, n), y = n)) +
+  geom_bar(stat = "identity", fill = "pink") +
+  coord_flip() +
+  scale_y_continuous(labels = comma) +
+  labs(title = "Top 10 Job Titles", x = "Job Title", y = "Count")
+# Save the plot
+ggsave(filename = "results/figures/top10_soc_title.png", plot = p1, width = 8, height = 6)
 
-## ---- fitfig1 --------
[…]

### 2025-03-14 products/manuscript/Manuscript.qmd
part 3 commit 1

@@
 ## Statistical analysis
-Various plots will be made to visualize the data. Linear regression will be used to analyze the relationship between variables. Machine learning methods will be used as modeling technique.
+Various plots were created to visualize the data. Classification models were used to analyze the categorical outcome.
 
@@
 The @fig-top10_emp_state presents the 10 states with the most applications, with California recording over 600,000 cases.
-Meanwhile, the @fig-distribution_PREV_WAGE plot illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
+Meanwhile, the @fig-distribution_PREV_WAGE illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
 ```{r}
@@
 
-The @fig-wage_by_soc_title plot shows the 10 job titles with the highest median wage, and they are all medical practitioners.
-The @fig-wage_by_employer plot highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing.
-The @fig-wage_by_state plot indicates that Washington has the highest median wage by state.
+The @fig-wage_by_soc_title shows the 10 job titles with the highest median wage, and they are all medical practitioners.
+The @fig-wage_by_employer highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing.
+The @fig-wage_by_state indicates that Washington has the highest median wage by state.
 Plots for the 10 lowest median wages are provided in Supplement Figures 1–3.
-The @fig-remote_trend_absolute plot illustrates the trend of remote work over the years.
+The @fig-remote_trend_absolute illustrates the trend of remote work over the years.
 The number of remote work cases surged from 2019 to 2020 due to the pandemic and remained relatively stable from 2020 to 2023.
@@
 ## Basic statistical analysis
+### Bivariate Analysis
+The variable WAGE_RATE_OF_PAY_FROM was selected as the outcome of interest to study the wages of H-1B workers.
+I first conducted a bivariate analysis to identify potential predictor variables.
+To perform the analysis, I selected a half-month subset of the data.
+
+The @fig-distribution_WAGE_Jan2024 illustrates a histogram of wage distribution during January 1–15, 2024.
+The continuous wage variable was categorized into four ranges: "(0, 75,000)", "(75,000, 150,000)", "(150,000, 225,000)", and "Above 225,000", converting it into a categorical variable.
+
+A random forest model was applied for classification using a single predictor, with 1,380 observations in the training set and 346 observations in the testing set.
+@tbl-combined_accuracy1 to @tbl-combined_accuracy4 summarize the model fit for the predictors: job title (SOC_TITLE), employer location (EMPLOYER_STATE), worksite location (WORKSITE_STATE), and employer (EMPLOYER_NAME).
+The results indicate that these variables exhibit moderate predictive performance.
+
+Next, a multivariate random forest model was developed. @tbl-combined_accuracy_all shows that the multivariate model outperformed the bivariate models.
+
+In the next step, different classification algorithms will be explored to further enhance model performance. Additionally, cross-validation will be incorporated to improve model reliability.
+```{r}
+#| label: fig-distribution_WAGE_Jan2024
+#| fig-cap: "Distribution of Wages (January 1–15, 2024)."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","distribution_WAGE_Jan2024.png"))
+```
+
+```{r}
+#| label: tbl-combined_accuracy1
+#| tbl-cap: "Model Fit for Wage Based on Job Title."
+#| echo: FALSE
+table1 = readRDS(here("results","tables","combined_accuracy1.rds"))
+knitr::kable(table1)
+```
+
+```{r}
+#| label: tbl-combined_accuracy2
+#| tbl-cap: "Model Fit for Wage Based on Employer Locations."
+#| echo: FALSE
+table2 = readRDS(here("results","tables","combined_accuracy2.rds"))
+knitr::kable(table2)
+```
+
+```{r}
+#| label: tbl-combined_accuracy3
+#| tbl-cap: "Model Fit for Wage Based on Worksite Locations."
+#| echo: FALSE
+table3 = readRDS(here("results","tables","combined_accuracy3.rds"))
+knitr::kable(table3)
+```
+
+```{r}
+#| label: tbl-combined_accuracy4
+#| tbl-cap: "Model Fit for Wage Based on Employer."
+#| echo: FALSE
+table4 = readRDS(here("results","tables","combined_accuracy4.rds"))
+knitr::kable(table4)
+```
+
+```{r}
+#| label: tbl-combined_accuracy_all
+#| tbl-cap: "Model Fit for Wage Based on Job Title, Employer Location, Worksite Location, and Employer."
+#| echo: FALSE
+table5 = readRDS(here("results","tables","combined_accuracy_all.rds"))
+knitr::kable(table5)
+```
 

### 2025-03-14 code/analysis-code/statistical-analysis.R

@@ -1,56 +1,298 @@
-###############################
-# analysis script
-#
-#this script loads the processed, cleaned data, does a simple analysis
-#and saves the results to the results folder
+# Choose WAGE_RATE_OF_PAY_FROM as the outcome of interest to study the wages of H-1B workers
 
-#load needed packages. make sure they are installed.
-library(ggplot2) #for plotting
-library(broom) #for cleaning up output from lm()
-library(here) #for data loading/saving
+# Load package
+library(tidymodels)
+library(dplyr)
+library(lubridate)
+library(embed)
+library(here)
+library(ggplot2)
 
-#path to data
-#note the use of the here() package and not absolute paths
-data_location <- here::here("data","processed-data","processeddata.rds")
+# Load the data
+LCAwage <- readRDS(here("data", "processed-data", "LCAwage.rds"))
 
-#load data. 
-mydata <- readRDS(data_location)
+# Filter for January 2024 using RECEIVED_DATE and convert predictors to factors
+LCAwage_Jan2024 <- LCAwage %>% 
+  filter(year(RECEIVED_DATE) == 2024, month(RECEIVED_DATE) == 1, , day(RECEIVED_DATE) == c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15)) %>%
+  mutate(
+    SOC_TITLE = as.factor(SOC_TITLE),
+    EMPLOYER_STATE = as.factor(EMPLOYER_STATE),
+    WORKSITE_STATE = as.factor(WORKSITE_STATE),
+    EMPLOYER_NAME = as.factor(EMPLOYER_NAME)
+  )
+
+# Make histogram to visualize distribution
+hist_wage<-ggplot(LCAwage_Jan2024, aes(x = WAGE_RATE_OF_PAY_FROM)) +
+  geom_histogram(binwidth = 5000, fill = "pink", color = "black") +
+  scale_x_continuous(labels = comma) +
+  labs(title = "Distribution of Wage", x = "Wage", y = "Frequency")
+ggsave(filename = "results/figures/distribution_WAGE_Jan2024.png", plot = hist_wage, width = 8, height = 6)
+
+# Create a categorical variable for wage ranges
+LCAwage_Jan2024 <- LCAwage_Jan2024 %>%
+  mutate(WAGE_CAT = cut(
+    WAGE_RATE_OF_PAY_FROM,
+    breaks = c(0, 75000, 150000, 225000, Inf),
[…]

### 2025-03-14 code/eda-code/edacode.R

@@ -57,6 +57,9 @@ ggsave(filename = "results/figures/top10_emp_state.png", plot = p3, width = 8, h
 # Wage units were standardized by retaining only observations where WAGE_UNIT_OF_PAY and PW_UNIT_OF_PAY were specified as "Year", ensuring consistency in wage comparisons.
 LCAwage <- LCAdata %>%
   filter(WAGE_UNIT_OF_PAY == "Year", PW_UNIT_OF_PAY == "Year")
+# Save as rds
+save_data_location <- here::here("data","processed-data","LCAwage.rds")
+saveRDS(LCAwage, file = save_data_location)
 
 # Distribution of PREVAILING_WAGE
 p4<-ggplot(LCAwage, aes(x = PREVAILING_WAGE)) +

### 2025-04-02 products/manuscript/Manuscript.qmd
Part 4 commit 1

@@
 ---
-title: "Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)"
+title: "Working Status Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)"
 author: "Yufei Wu"
@@
 # Summary/Abstract
+To be added.
 
@@
 As USCIS is receiving more and more H-1B registration these years, it's harder for a foreign worker to get an H-1B visa.
-The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [@LaborConditionApplication2025].
+The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B.
 The LCA contains essential details such as job title, wage, and location about the proposed H-1B employment.
-Therefore, analyzing the LCA data can provide some ideas on the H-1B application status.
-
-## Description of data and data source
-
-The data is H1B LCA Disclosure Data (2020-2024) from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data).
-It contains LCA disclosure datasets from U.S.
-Department of Labor, covering the period from 2020 to 2024, and includes information such as case status, job title, Standard Occupational Classification (SOC) title, location, and wages.
+Therefore, analyzing the LCA data can provide some ideas on the H-1B application status [@mahajan2024impact].
 
@@
 
-The dataset used in this analysis is the H1B LCA Disclosure Data (2020-2024) from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data).
-It comprises labor condition application (LCA) disclosure records from the U.S.
-Department of Labor, covering the period from 2020 to 2024.
-The dataset includes key information such as case status, job title, Standard Occupational Classification (SOC) title, employer details, location, and wages.
+The dataset is H1B LCA Disclosure Data (2020-2024) from the U.S.
+Department of Labor.
+The data is provided by employers and includes final determinations issued by the Department’s Office of Foreign Labor Certification (OFLC) under the Employment and Training Administration (ETA).
+It includes information such as case status, job title, Standard Occupational Classification (SOC) title, location, and wages.
+It can be easily downloaded from [Kaggle](https://www.kaggle.com/datasets/zongaobian/h1b-lca-disclosure-data-2020-2024/data).
 
@@
 ## Statistical analysis
-Various plots were created to visualize the data. Classification models were used to analyze the categorical outcome.
+
+### Exploratory/Descriptive Analysis
+The method began with an exploratory analysis to assess the overall structure of the dataset.
+Univariate techniques were applied to examine the distribution of key variables, such as job titles, employers, and geographic locations, by analyzing application counts over a multi-year period.
+Additionally, the distribution of prevailing wages was evaluated using visualizations to understand the range and concentration of wage values.
+
+### Initial Statistical Analysis
+For the initial statistical analysis, a half-month subset of the data (from January 1–15, 2024) was selected.
+The continuous wage variable was then converted into categorical ranges to facilitate further analysis.
+Bivariate analyses were conducted using Random Forest classification models with individual predictors, including SOC title, employer location, worksite location, and employer name.
+These single predictor models were compared against a null model to assess their predictive utility.
+
+### Full Analysis
+In the full analysis phase, multiple advanced modeling techniques were employed to predict wages.
+The methodology involved developing models using Random Forest, XGBoost, and SVM, with a comprehensive cross-validation approach (5-fold with 5 repetitions) to ensure robust evaluation.
+A comparative analysis of the training and test performance of these models was carried out to identify the approach that best balanced model complexity and generalization capability for wage prediction.
 
@@
 
-## Basic statistical analysis
-### Bivariate Analysis
-The variable WAGE_RATE_OF_PAY_FROM was selected as the outcome of interest to study the wages of H-1B workers.
+## Initial statistical analysis
+
+The variable wage was selected as the outcome of interest to study the wages of H-1B workers.
 I first conducted a bivariate analysis to identify potential predictor variables.
@@
 A random forest model was applied for classification using a single predictor, with 1,380 observations in the training set and 346 observations in the testing set.
-@tbl-combined_accuracy1 to @tbl-combined_accuracy4 summarize the model fit for the predictors: job title (SOC_TITLE), employer location (EMPLOYER_STATE), worksite location (WORKSITE_STATE), and employer (EMPLOYER_NAME).
+@tbl-combined_accuracy1 to @tbl-combined_accuracy4 summarize the model fit for the predictors: SOC title, employer location, worksite location, and employer name.
 The results indicate that these variables exhibit moderate predictive performance.
@@
 
-In the next step, different classification algorithms will be explored to further enhance model performance. Additionally, cross-validation will be incorporated to improve model reliability.
+All the models performed better than null model (@tbl-combined_null_accuracy), with the multivariate model performed best.
 ```{r}
@@
 
+```{r}
+#| label: tbl-combined_null_accuracy
+#| tbl-cap: "Null Model."
+#| echo: FALSE
+table6 = readRDS(here("results","tables","combined_null_accuracy.rds"))
+knitr::kable(table6)
+```
+
 ## Full analysis
+
+The initial statistical analysis shows that variables SOC title, employer location, worksite location, and employer name can serve as predictors for outcome variable wage.
+Based on that, Random Forest, XGBoost, and SVM were used to fit the model, including cross-validation (5-fold and 5 times repetition).
+
+Tables summarizing the performance of the three models can be found in Supplement Table 2-4.
+@fig-model_compare shows the cmoparison of model performance among Random Forest, XGBoost, and SVM.
+SVM achieves the highest accuracy on the training data (0.886), while Random Forest (0.820) and XGBoost (0.738) show slightly lower training accuracy compared to SVM.
+On the test set, random forest outperform among the three models with an accuracy of 0.740.
+The SVM model's high training performance compared with its relatively lower test performance (0.717) indicates that it might be capturing noise or very specific patterns in the training data that do not carry over to unseen data.
+In contrast, Random Forest keeps a better balance between fitting the training data and maintaining generalization on the test data.
+Therefore, the Random Forest model can be chosen to predict the wage since it appears more robust on the test data.
+
+```{r}
+#| label: fig-model_compare
+#| fig-cap: "Comparison of Model Performance: Random Forest, XGBoost, and SVM."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","model_compare.png"))
+```
 

### 2025-04-02 products/manuscript/supplement/Supplementary-Material.qmd
Part 4 commit 1

@@
 # Additional results
+## Exploratory/Descriptive analysis
 
@@
 
+## Model Fitting
+
+@tbl-rf_combined_accuracy_cv_default to @tbl-combined_accuracy_cv_svm show the model accuracy in both training and test data of the three models: Random Forest, XGBoost, and SVM.
+
+```{r}
+#| label: tbl-rf_combined_accuracy_cv_default
+#| tbl-cap: "Accuracy of Random Forest."
+#| echo: FALSE
+table2 = readRDS(here("results","tables","rf_combined_accuracy_cv_default.rds"))
+knitr::kable(table2)
+```
+
+```{r}
+#| label: tbl-combined_accuracy_cv_xgb_reg
+#| tbl-cap: "Accuracy of XGBoost."
+#| echo: FALSE
+table3 = readRDS(here("results","tables","combined_accuracy_cv_xgb_reg.rds"))
+knitr::kable(table3)
+```
+
+```{r}
+#| label: tbl-combined_accuracy_cv_svm
+#| tbl-cap: "Accuracy of SVM."
+#| echo: FALSE
+table4 = readRDS(here("results","tables","combined_accuracy_cv_svm.rds"))
+knitr::kable(table4)
+```
+
 {{< pagebreak >}}

### 2025-04-02 code/analysis-code/full analysis.R

@@ -1,0 +1,241 @@
+# Load packages
+library(tidymodels)
+library(dplyr)
+library(lubridate)
+library(embed)
+library(here)
+library(ggplot2)
+#install.packages("xgboost")
+#install.packages("kernlab")
+
+# Load data
+LCAwage_Jan2024 <- readRDS(here("data", "processed-data", "LCAwage_Jan2024.rds"))
+
+# Split the data into training (80%) and testing (20%) sets
+set.seed(123)
+data_split <- initial_split(LCAwage_Jan2024, prop = 0.8, strata = WAGE_CAT)
+train_data <- training(data_split)
+test_data  <- testing(data_split)
+
+
+# 1. Random forest model
+# --- Define the Recipe for the Random Forest Model with Default Hyperparameters ---
+rf_default_class_recipe <- recipe(WAGE_CAT ~ SOC_TITLE + EMPLOYER_STATE + WORKSITE_STATE + EMPLOYER_NAME, data = train_data) %>%
+  step_dummy(all_nominal_predictors(), one_hot = TRUE)
+
+# --- Specify the Random Forest Model with Default Hyperparameters ---
+# Defaults: mtry = floor(sqrt(p)), min_n = 1, trees = 500
+rf_default_class_spec <- rand_forest() %>% 
+  set_engine("ranger") %>% 
+  set_mode("classification")
+
+# --- Create the Workflow ---
+rf_default_class_workflow <- workflow() %>%
+  add_recipe(rf_default_class_recipe) %>%
+  add_model(rf_default_class_spec)
+
+# --- Set Up Cross-Validation ---
+# 5-fold cross-validation repeated 5 times (total of 25 resamples)
+set.seed(123)
+rf_default_cv_folds <- vfold_cv(train_data, v = 5, repeats = 5)
+
+# --- Fit the Model with Cross-Validation ---
+rf_default_cv_results <- fit_resamples(
+  rf_default_class_workflow,
+  resamples = rf_default_cv_folds,
+  metrics = metric_set(accuracy)
+)
+
+# Collect and print cross-validation metrics
+rf_default_cv_metrics <- collect_metrics(rf_default_cv_results)
+print(rf_default_cv_metrics)
+
+# --- Fit the Final Model on the Entire Training Data ---
+rf_default_final_fit <- rf_default_class_workflow %>% fit(data = train_data)
+
+# --- Evaluate on the Training Data ---
[…]

### 2025-04-02 code/analysis-code/initial analysis.R

@@ -7,6 +7,9 @@ library(lubridate)
 library(embed)
 library(here)
 library(ggplot2)
+library(scales)
+library(rsample)
+#install.packages("ranger")
 
 # Load the data
 LCAwage <- readRDS(here("data", "processed-data", "LCAwage.rds"))
@@ -37,6 +40,9 @@ LCAwage_Jan2024 <- LCAwage_Jan2024 %>%
     right = FALSE
   ))
 head(LCAwage_Jan2024)
+
+save_data_location <- here::here("data","processed-data","LCAwage_Jan2024.rds")
+saveRDS(LCAwage_Jan2024, file = save_data_location)
 
 # Split the data into training (80%) and testing (20%) sets
 set.seed(123)
@@ -296,3 +302,54 @@ combined_accuracy_all
 # save as rds
 saveRDS(combined_accuracy_all, file = "results/tables/combined_accuracy_all.rds")
 
+
+# Fit a null model for comparison
+
+# Create a recipe that only includes an intercept (i.e. no predictors)
+null_recipe <- recipe(WAGE_CAT ~ 1, data = train_data)
+
+# Specify a null model for classification using the parsnip engine
+null_spec <- null_model(mode = "classification") %>%
+  set_engine("parsnip")
+
+# Combine the recipe and the null model into a workflow
+null_workflow <- workflow() %>%
+  add_recipe(null_recipe) %>%
+  add_model(null_spec)
+
+# Fit the null model on the training data
+null_fit <- null_workflow %>% fit(data = train_data)
+
+# Generate predictions on the test data and bind them with test_data
+null_test_predictions <- test_data %>% 
+  bind_cols(
+    predict(null_fit, test_data),
+    predict(null_fit, test_data, type = "prob")
+  )
+
+# Evaluate accuracy on the test data and label the dataset
+null_test_accuracy <- null_test_predictions %>%
+  accuracy(truth = WAGE_CAT, estimate = .pred_class) %>%
+  mutate(dataset = "Test")
+
+# Generate predictions on the training data and bind them with train_data
+null_train_predictions <- train_data %>% 
+  bind_cols(
+    predict(null_fit, train_data),
+    predict(null_fit, train_data, type = "prob")
+  )
+
+# Evaluate accuracy on the training data and label the dataset
+null_train_accuracy <- null_train_predictions %>%
+  accuracy(truth = WAGE_CAT, estimate = .pred_class) %>%
+  mutate(dataset = "Train")
+
[…]

### 2025-04-18 products/manuscript/Manuscript.qmd
Part 5 commit 1

@@
 # Summary/Abstract
-To be added.
+Background: The H-1B visa allows U.S.
+employers to hire foreign workers in specialized fields like technology, engineering, and medical sciences.
+It requires a bachelor’s degree or equivalent and typically lasts up to six years.
+Annually, 65,000 visas are available, with an additional 20,000 for candidates with U.S.
+master’s or doctorate degrees.
+Due to increasing applications, a lottery system determines who can file an H-1B petition.
+Employers must file a Labor Condition Application (LCA), detailing job title, wage, and location, as a prerequisite for H-1B approval.
+Analyzing LCA data can offer insights into H-1B application trends.
+
+Data: This project uses LCA disclosure datasets from the U.S.
+Department of Labor, covering the period from 2020 to 2024.
+The data is provided by employers and includes final determinations issued by the Department’s Office of Foreign Labor Certification (OFLC) under the Employment and Training Administration (ETA).
+The dataset contains key variables such as job title, wage, and employer information for H-1B workers, making it useful for analyzing their employment status.
+
+Methods: The analysis began by cleaning and filtering the H1B LCA Disclosure Data (2020–2024) to include only certified H-1B cases, focusing on key variables such as job titles, employer details, and wages.
+Univariate analysis was conducted to identify the most common job titles, top employers, and states with the highest number of applications, along with analyzing wage distributions.
+Bivariate analysis followed, examining median wages across different job titles, employers, and states, and tracking remote work trends before and after the pandemic.
+Predictive modelling was carried out only on a half‑month slice of the data (1–15 January 2024).
+Wages were binned into four ordered categories.
+Single‑predictor random‑forest classifiers (SOC title, employer state, work‑site state, employer) and a multivariate random‑forest model were trained, followed by three multivariate algorithms (Random Forest, XGBoost, and Support‑Vector Machine), evaluated with 5×5 repeated cross‑validation.
+Accuracy was the main metric; final models were refit on the 80% training portion of the slice and scored on the 20% hold‑out test set.
+
+Results: Within the modelling slice, each single‑predictor forest out‑performed a null model (test accuracy ≈ 0.62–0.68).
+The multivariate forest improved test accuracy to 0.73.
+Among the three advanced models, Support‑Vector Machine attained the highest training accuracy (0.886) but lower test accuracy (0.717), indicating over‑fitting.
+Random Forest achieved the best balance between fit and generalisation (train=0.820; test=0.740) and was selected as the preferred wage‑prediction model for this data slice.
 
@@
 
-The @fig-top10_soc_title displays the 10 job titles with the highest number of applications filed between 2020 and 2024, with "Software Developers, Applications" leading at over 500,000 cases.
-The @fig-top10_emp_name highlights the top 10 employers by application count, with "COGNIZANT TECHNOLOGY SOLUTIONS US CORP" topping the list at approximately 93,000 cases.
-The @fig-top10_emp_state presents the 10 states with the most applications, with California recording over 600,000 cases.
-Meanwhile, the @fig-distribution_PREV_WAGE illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
+The @fig-univariate_analysis_panel_with_labels (a) displays the 10 job titles with the highest number of applications filed between 2020 and 2024, with "Software Developers, Applications" leading at over 500,000 cases.
+The @fig-univariate_analysis_panel_with_labels (b) highlights the top 10 employers by application count, with "COGNIZANT TECHNOLOGY SOLUTIONS US CORP" topping the list at approximately 93,000 cases.
+The @fig-univariate_analysis_panel_with_labels (c) presents the 10 states with the most applications, with California recording over 600,000 cases.
+Meanwhile, the @fig-univariate_analysis_panel_with_labels (d) illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
 ```{r}
-#| label: fig-top10_soc_title
-#| fig-cap: "Top 10 Job Titles."
+#| label: fig-univariate_analysis_panel_with_labels
+#| fig-cap: "Univariate Analysis: Distribution Analysis."
 #| echo: FALSE
-knitr::include_graphics(here("results","figures","top10_soc_title.png"))
-```
-
-```{r}
-#| label: fig-top10_emp_name
-#| fig-cap: "Top 10 Employers."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","top10_emp_name.png"))
-```
-
-```{r}
-#| label: fig-top10_emp_state
-#| fig-cap: "Top 10 Employer Locations."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","top10_emp_state.png"))
-```
-
-```{r}
-#| label: fig-distribution_PREV_WAGE
-#| fig-cap: "Distribution of Prevailing Wage."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","distribution_PREV_WAGE.png"))
+knitr::include_graphics(here("results","figures","univariate_analysis_panel_with_labels.png"))
 ```
@@
 
-The @fig-wage_by_soc_title shows the 10 job titles with the highest median wage, and they are all medical practitioners.
-The @fig-wage_by_employer highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing.
-The @fig-wage_by_state indicates that Washington has the highest median wage by state.
+The @fig-bivariate_analysis_panel_with_labels (a) shows the 10 job titles with the highest median wage, and they are all medical practitioners.
+The @fig-bivariate_analysis_panel_with_labels (b) highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing.
+The @fig-bivariate_analysis_panel_with_labels (c) indicates that Washington has the highest median wage by state.
 Plots for the 10 lowest median wages are provided in Supplement Figures 1–3.
-The @fig-remote_trend_absolute illustrates the trend of remote work over the years.
+The @fig-bivariate_analysis_panel_with_labels (d) illustrates the trend of remote work over the years.
 The number of remote work cases surged from 2019 to 2020 due to the pandemic and remained relatively stable from 2020 to 2023.
@@
 ```{r}
-#| label: fig-wage_by_soc_title
-#| fig-cap: "Top 10 Job Titles by Highest Median Wage."
+#| label: fig-bivariate_analysis_panel_with_labels
+#| fig-cap: "Bivariate Analysis."
 #| echo: FALSE
-knitr::include_graphics(here("results","figures","wage_by_soc_title.png"))
-```
-
-```{r}
-#| label: fig-wage_by_employer
-#| fig-cap: "Top 10 Employers by Highest Median Wage."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","wage_by_employer.png"))
-```
-
-```{r}
-#| label: fig-wage_by_state
-#| fig-cap: "Top 10 States by Highest Median Wage."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","wage_by_state.png"))
-```
-
-```{r}
-#| label: fig-remote_trend_absolute
-#| fig-cap: "Remote Work Trends Over Years."
-#| echo: FALSE
-knitr::include_graphics(here("results","figures","remote_trend_absolute.png"))
+knitr::include_graphics(here("results","figures","bivariate_analysis_panel_with_labels.png"))
 ```
@@
 Tables summarizing the performance of the three models can be found in Supplement Table 2-4.
+CV accuracy distribution for different models can be found in Supplement Figure 4.
 @fig-model_compare shows the cmoparison of model performance among Random Forest, XGBoost, and SVM.
@@
 
-## Summary and Interpretation
+## Labor-market findings
+The exploratory results clearly showed the dominance of the technology sector in H-1B employment, especially the role of “Software Developers, Applications,” with over 500,000 cases.
+California was identified as the primary destination state.
+Interestingly, however, higher median wages were found predominantly among medical occupations and employers in healthcare and financial industries, rather than the technology sector itself.
+Washington state showed the highest median wage, likely because of the presence of major technology and e-commerce companies.
 
-## Strengths and Limitations
+The analysis of remote-work cases indicated a sharp increase during 2020, driven by the pandemic.
+This trend remained relatively stable until a slight decrease in 2024.
+The persistence of remote-work practices suggests that flexible work arrangements have become established in the H-1B landscape, although the method used to identify remote work (differences between employer and worksite states) may underestimate actual prevalence.
 
-## Conclusions
+## Predictive modeling performance
+Predictive modeling using a half-month subset (January 1–15, 2024) showed promising results.
+Single-predictor random-forest models revealed that the employer’s identity alone significantly influenced wage predictions, indicating substantial pay differences among employers.
+Geographic location also had a meaningful effect.
+A multivariate random-forest model achieved improved test accuracy (0.73), and among the three advanced models tested—Random Forest, XGBoost, and SVM—the Random Forest model offered the best balance between accuracy on training data (0.82) and generalization on test data (0.74).
+This suggests that Random Forest is well-suited for predicting wage categories from this type of data.
+
+## Limitations and future directions
+There are several limitations in this study.
+First, predictive modeling was conducted using only a brief half-month period due to computational memory constraints, which limits generalizability to broader timeframes.
+Second, converting continuous wages into four broad categories simplifies the analysis but sacrifices detailed wage information.
+Future studies should consider expanding the analysis to larger, longer-term datasets.
+Exploring continuous-wage prediction models, using more sophisticated techniques for handling class imbalance, and analyzing textual information from job titles might enhance model accuracy.
+
+# Conclusions
+
+This study analyzed certified H-1B visa cases from 2020 to 2024, highlighting key trends in job titles, wages, and remote-work patterns.
+Predictive modeling demonstrated that a Random Forest classifier effectively predicts wage categories based on employer, occupation, and geographic location.
+Although limited by using a short time frame and categorized wage data, this approach provides a useful baseline for wage prediction.
+Future studies expanding dataset size, analyzing continuous wages, and including additional factors could further improve predictive accuracy and provide deeper insights into H-1B employment patterns.
 

### 2025-04-18 products/manuscript/supplement/Supplementary-Material.qmd
Part 5 commit 1

@@
 
-# Discussion
+## Full analysis
+
+@fig-cv_accuracy_distribution_panel shows CV accuracy distribution for different models.
+```{r}
+#| label: fig-cv_accuracy_distribution_panel
+#| fig-cap: "CV accuracy distribution for different models."
+#| echo: FALSE
+knitr::include_graphics(here("results","figures","cv_accuracy_distribution_panel.png"))
+```
 

### 2025-04-18 code/analysis-code/full analysis.R

@@ -5,8 +5,11 @@ library(lubridate)
 library(embed)
 library(here)
 library(ggplot2)
+library(stringr)
+library(patchwork)
 #install.packages("xgboost")
 #install.packages("kernlab")
+
 
 # Load data
 LCAwage_Jan2024 <- readRDS(here("data", "processed-data", "LCAwage_Jan2024.rds"))
@@ -82,6 +85,21 @@ print(rf_default_combined_accuracy)
 saveRDS(rf_default_combined_accuracy, file = "results/tables/rf_combined_accuracy_cv_default.rds")
 
 
+
+# Extract per‑resample accuracies
+
+cv_acc_resample <- rf_default_cv_results %>%
+  collect_metrics(summarize = FALSE) %>% 
+  filter(.metric == "accuracy") %>% 
+  mutate(
+    fold = str_extract(id, "(?<=Fold)\\d+"),     # Fold 1 … 5
+    rep  = str_extract(id, "(?<=Repeat)\\d+")    # Repeat 1 … 5
+  )
+
+
+
+
+
 # 2. XGBoot model
 # --- Define the Recipe for the XGBoost Model with Regularization ---
 # Use all predictors and one-hot encode them
@@ -152,6 +170,19 @@ print(xgb_reg_combined_accuracy)
 saveRDS(xgb_reg_combined_accuracy, file = "results/tables/combined_accuracy_cv_xgb_reg.rds")
 
 
+# Per‑resample accuracies (25 rows)
+xgb_cv_acc_resample <- xgb_reg_cv_results %>%
+  collect_metrics(summarize = FALSE) %>%          # keep every resample
+  filter(.metric == "accuracy") %>% 
+  mutate(
+    fold = str_extract(id, "(?<=Fold)\\d+"),      # Fold 1 … 5
+    rep  = str_extract(id, "(?<=Repeat)\\d+")     # Repeat 1 … 5
+  )
+
+
+
+
+
 # 3. SVM
 # --- Define the Recipe for the SVM Model ---
 # Use all predictors, one-hot encode them, and normalize the numeric predictors.
@@ -217,10 +248,11 @@ print(svm_combined_accuracy)
 # save as rds
 saveRDS(svm_combined_accuracy, file = "results/tables/combined_accuracy_cv_svm.rds")
 
+
 # Make plot
 # Add a column to indicate the model type for each set of results
 rf_acc   <- rf_default_combined_accuracy %>% mutate(model = "Random Forest")
[…]

### 2025-04-18 code/eda-code/edacode.R

@@ -4,7 +4,8 @@ library(here)
 library(dplyr)
 library(scales)
 library(lubridate)
-
+library(gridExtra)
+library(grid)
 
 # load data
 LCAdata <- readRDS(here("data", "processed-data", "LCAdata.rds"))
@@ -257,4 +258,37 @@ p_remote_abs <- ggplot(remote_trends_abs, aes(x = year, y = remote_count)) +
 # Save the plot
 dir.create("results/figures", recursive = TRUE, showWarnings = FALSE)
 ggsave(filename = "results/figures/remote_trend_absolute.png", plot = p_remote_abs, width = 8, height = 6)
+
+
+# Function to add labels to a plot
+add_label <- function(plot, label) {
+  plot + annotation_custom(grob = textGrob(label, x = unit(0.03, "npc"), y = unit(0.98, "npc"), 
+                                           gp = gpar(fontsize = 10, fontface = "bold")))
+}
+
+# Add labels to each plot
+p1_labeled <- add_label(p1, "(a)")
+p2_labeled <- add_label(p2, "(b)")
+p3_labeled <- add_label(p3, "(c)")
+p4_labeled <- add_label(p4, "(d)")
+
+# Univariate Analysis: Distribution Analysis with labels
+univariate_panel <- grid.arrange(p1_labeled, p2_labeled, p3_labeled, p4_labeled, ncol = 2, 
+                                 top = "Univariate Analysis: Distribution Analysis")
+
+# Save the univariate panel with labels
+ggsave(filename = "results/figures/univariate_analysis_panel_with_labels.png", plot = univariate_panel, width = 12, height = 10)
+
+# Add labels to the bivariate plots
+p5_labeled <- add_label(p5, "(a)")
+p6_labeled <- add_label(p6, "(b)")
+p7_labeled <- add_label(p7, "(c)")
+p_remote_abs_labeled <- add_label(p_remote_abs, "(d)")
+
+# Bivariate Analysis with labels
+bivariate_panel <- grid.arrange(p5_labeled, p6_labeled, p7_labeled, p_remote_abs_labeled, ncol = 2, 
+                                top = "Bivariate Analysis")
+
+# Save the bivariate panel with labels
+ggsave(filename = "results/figures/bivariate_analysis_panel_with_labels.png", plot = bivariate_panel, width = 12, height = 10)
 
